---
title: checked
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README",
  out.width = "100%",
  asciicast_theme = if (Sys.getenv("IN_PKGDOWN") == "true") {
    "pkgdown"
  } else {
    "readme"
  }
)

asciicast::init_knitr_engine(
  startup = bquote({
    options(repos = .(getOption("repos")))
  }),
  echo_input = FALSE
)
```

> Batch `R CMD check` management

<!-- badges: start -->
[![R-CMD-check](https://github.com/Genentech/checked/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Genentech/checked/actions/workflows/R-CMD-check.yaml/badge.svg)
[![CRAN](https://img.shields.io/cran/v/checked.svg)](https://cran.r-project.org/package=checked)
[![coverage](https://codecov.io/gh/Genentech/checked/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Genentech/checked/tree/main)
<!-- badges: end -->

```{sh clone-dev-praise, echo = FALSE, results = "hide"}
# praise chosen for having few direct and reverse dependencies
rm -rf /tmp/praise
git clone https://github.com/gaborcsardi/praise /tmp/praise
```

# Running Checks

Although `checked` is broadly capable of running arbitrary sets of `R CMD check`
tasks, reverse dependency checking is one of the most common use cases where
batch `R CMD check`s are needed. 

Running reverse dependency checks is as easy as

```r
library(checked)
x <- run("/home/dev/praise")
results(x)
```
```{r, echo = FALSE}
library(checked)
x <- run("/tmp/praise", reporter = NULL)
results(x)
```

## Monitoring Runs

Because running many checks in parallel can be a difficult process to monitor,
capable interfaces will provide a convenient output for tracking various
runs, check results and package installations; keeping a log of any issues 
that might arise during the process.

If your editor doesn't support the full output, you might consider launching
your checks in a terminal which should be less constrained. This would also
free up your preferred editor for you to use while your checks run.

```r
library(checked)
run("/home/dev/praise")
```
```{asciicast ansi-tty-example, cache = TRUE}
#| asciicast_knitr_output = "svg",
#| asciicast_at = "all",
#| asciicast_cursor = FALSE
options(checked.tty_tick_interval = 200)
checked::run("/tmp/praise")
cat()
```
